---
title: "Table 3: Cox (UVA)"
author: "Jessica George"
date: "01/29/22"
output:
  html_document:
    toc: True
    toc_depth: 2
---

# Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(finalfit)
library(lubridate)
library(survival)
library(readxl)

source("../format_data.R")
```


# Data
```{r echo=TRUE, message=FALSE, warning=FALSE}
original <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)

# grab RT/CRT patients only
data <- original %>% 
  filter(rt == "Yes" | crt == "Yes")
```

# Univariate Results
```{r echo=TRUE, message=FALSE, warning=FALSE}
run_univariate <- function(data, additional_predictors=c()) {
  dependent <- "Surv(time_alive_treat, vital_status)"
  
  uni_predictors <- c("enroll_age", "age_cat", "marital", "distance_factored2", 
                      "init_performance_status", "hiv_status", "hiv_cd4_cat", "hiv_cd4_cat2", 
                      "cr_result", "cr_result_s100", "hb_result", "wbc_result", "wbc_result_s100", 
                      "neut_result", "neut_result_s100", "alb_result", "alb_result_s100", 
                      "combined_cancer_stage", "combined_cancer_stage2", "combined_cancer_stage3", 
                      "total_chemo_received_cat", "total_chemo_received_4", "chemo", "eqd2", 
                      "eqd2_75", "eqd2_79", "eqd2_80", "pathology_group", "pathology_group2", 
                      "pathology_group3", "cancer_screening", "treat_response", "hiv_cd4_cat", 
                      "hiv_cd4_cat2", "curative_palliative")
  
  uni_predictors <- c(uni_predictors, additional_predictors)
  
  data %>%
    finalfit(dependent, uni_predictors) %>%
    select("Dependent: Surv(time_alive_treat, vital_status)", " ", "all", "HR (univariable)") %>% 
    knitr::kable()
}
```


# Overall Survival
## All Patients
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% run_univariate(c("path_treatment_30", "path_treatment_60", 
                          "path_treatment_90", "path_treatment_120", 
                          "path_treatment_150", "path_treatment_180"))
```


## Subgroup (>=30 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_30 == ">=30") %>% 
  run_univariate()
```


## Subgroup (>=60 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_60 == ">=60") %>% 
  run_univariate()
```


## Subgroup (>=90 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_90 == "≥90 days") %>% 
  run_univariate()
```


## Subgroup (<90 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_90 == "<90 days") %>% 
  run_univariate()
```


## Subgroup (>=120 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_120 == ">=120") %>% 
  run_univariate()
```


## Subgroup (>=150 day delays)
```{r echo=TRUE, message=FALSE, warning=FALSE}
data %>% 
  filter(path_treatment_150 == ">=150") %>% 
  run_univariate()
```


## Subgroup (>=180 day delays)
```{r}
data %>% 
  filter(path_treatment_180 == ">=180") %>% 
  run_univariate()
```