---
title: "Article/Abstract 3 Survival Curves -- 2018 diagnosis"
author: "Jessica George"
date: "11/9/2021"
output: html_document
---

# Libraries
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(survival)
library(survminer)
library(DescTools)
library(patchwork)
library(lubridate)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE, include=FALSE}
data <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)

data <- data %>% 
  mutate(pathology_year = year(ymd(pathology_date)))

data_2018 <- data %>% filter(pathology_year == 2018)
```

# KMs on All Patients
## 1) Survival status by Delay (180 days)
```{r, fig.width = 8}
delay180_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data_2018)

delay180_plot <- ggsurvplot(fit = delay180_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (180 days)",
  break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <180 days", "Delay ≥180 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay180_plot$plot <- delay180_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay180_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay180_plot$table <- delay180_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay180_plot$table
```


# KMs on All Patients
## 2) Survival status by Delay (150 days)
```{r, fig.width = 8}
delay150_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data_2018)

delay150_plot <- ggsurvplot(fit = delay150_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (150 days)",
  break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <150 days", "Delay ≥150 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay150_plot$plot <- delay150_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay150_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay150_plot$table <- delay150_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay150_plot$table
```


# KMs on All Patients
## 3) Survival status by Delay (120 days)
```{r, fig.width = 8}
delay120_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data_2018)

delay120_plot <- ggsurvplot(fit = delay120_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (120 days)",
  break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <120 days", "Delay ≥120 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay120_plot$plot <- delay120_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay120_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay120_plot$table <- delay120_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay120_plot$table
```


# KMs on All Patients
## 4) Survival status by Delay (120 days) and Stage
```{r, fig.width = 8, fig.height = 4}
delay120_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage_exact_factored4, data_2018)

delay120_stage_plot <- ggsurvplot(fit = delay120_stage_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (120 days) and Stage",
  break.time.by = 3,
  palette = c("#E69F00", "#009E73", "#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("<120 days, Stage I-II", "<120 days, Stage III-IV", "≥120 days, Stage I-II", "≥120 days, Stage III-IV"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay120_stage_plot$plot <- delay120_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay120_stage_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay120_stage_plot$table <- delay120_stage_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay120_stage_plot$table
```


# KMs on All Patients
## 5) Survival status by Delay (90 days)
```{r, fig.width = 8}
delay90_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_2018)

delay90_plot <- ggsurvplot(fit = delay90_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (90 days)",
  #break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <90 days", "Delay ≥90 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")

delay90_plot$plot <- delay90_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay90_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay90_plot$table <- delay90_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay90_plot$table
```


# KMs on All Patients
## 6a) Survival status by Delay (90 days) and Stage
```{r, fig.width = 8, fig.height = 4}
delay90_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage_exact_factored4, data_2018)

delay90_stage_plot <- ggsurvplot(fit = delay90_stage_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (90 days) and Stage",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73", "#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("<90 days, Stage I-II", "<90 days, Stage III-IV", "≥90 days, Stage I-II", "≥90 days, Stage III-IV"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay90_stage_plot$plot <- delay90_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay90_stage_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay90_stage_plot$table <- delay90_stage_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay90_stage_plot$table
```

## 6b) Survival status by Delay (90 days) and Stage
```{r, fig.width = 16, fig.height=14}
data_stage1 <- data_2018 %>% filter(combined_cancer_stage_exact_factored == "I (IA, IA1, IA2, IB1*, IB2, IB3)")

delay90_stage1_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage1)

delay90_stage1_plot <- ggsurvplot(fit = delay90_stage1_survival,
  data_stage1,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates for Stage I by Delay (90 days)",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73"),
  color = "path_treatment_90",
  conf.int = FALSE,
  censor = TRUE,
  legend="none",
  #legend.title="",
  #legend.labs = c("<90 days", "≥90 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay90_stage1_plot$plot <- delay90_stage1_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

data_stage2 <- data_2018 %>% filter(combined_cancer_stage_exact_factored == "II (IIA / IIB)")

delay90_stage2_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage2)

delay90_stage2_plot <- ggsurvplot(fit = delay90_stage2_survival,
  data_stage2,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates for Stage II by Delay (90 days)",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73"),
  color = "path_treatment_90",
  conf.int = FALSE,
  censor = TRUE,
  legend="none",
  #legend.title="",
  #legend.labs = c("<90 days", "≥90 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay90_stage2_plot$plot <- delay90_stage2_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

data_stage3 <- data_2018 %>% filter(combined_cancer_stage_exact_factored == "III (IIIA / IIIB / IIIC)")

delay90_stage3_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage3)

delay90_stage3_plot <- ggsurvplot(fit = delay90_stage3_survival,
  data_stage3,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates for Stage III by Delay (90 days)",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73"),
  color = "path_treatment_90",
  conf.int = FALSE,
  censor = TRUE,
  legend="none",
  #legend.title="",
  #legend.labs = c("<90 days", "≥90 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay90_stage3_plot$plot <- delay90_stage3_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

data_stage4 <- data_2018 %>% filter(combined_cancer_stage_exact_factored == "IV (IVA / IVB)")

delay90_stage4_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage4)

delay90_stage4_plot <- ggsurvplot(fit = delay90_stage4_survival,
  data_stage4,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates for Stage IV by Delay (90 days)",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73"),
  color = "path_treatment_90",
  conf.int = FALSE,
  censor = TRUE,
  legend="none",
  #legend.title="",
  #legend.labs = c("<90 days", "≥90 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay90_stage4_plot$plot <- delay90_stage4_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay90_stage1_plot$plot + delay90_stage2_plot$plot + delay90_stage3_plot$plot + delay90_stage4_plot$plot +
  plot_layout(guides = 'collect') & theme(legend.title = element_blank(), legend.position = 'top')
```

# KMs on All Patients
## 5) Survival status by Delay (84 days)
```{r, fig.width = 8}
delay84_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84, data_2018)

delay84_plot <- ggsurvplot(fit = delay84_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (84 days)",
  #break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <84 days", "Delay ≥84 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")

delay84_plot$plot <- delay84_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay84_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay84_plot$table <- delay84_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay84_plot$table
```


# KMs on All Patients
## 6a) Survival status by Delay (84 days) and Stage
```{r, fig.width = 8, fig.height = 4}
delay84_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84 + combined_cancer_stage_exact_factored4, data_2018)

delay84_stage_plot <- ggsurvplot(fit = delay84_stage_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  #xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (84 days) and Stage",
  #break.time.by = 3,
  palette = c("#E69F00", "#009E73", "#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("<84 days, Stage I-II", "<84 days, Stage III-IV", "≥84 days, Stage I-II", "≥84 days, Stage III-IV"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable(),
  fun="cloglog")
delay84_stage_plot$plot <- delay84_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay84_stage_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay84_stage_plot$table <- delay84_stage_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay84_stage_plot$table
```


# KMs on All Patients
## 7) Survival status by Delay (60 days)
```{r, fig.width = 8}
delay60_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data_2018)

delay60_plot <- ggsurvplot(fit = delay60_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (60 days)",
  break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <60 days", "Delay ≥60 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay60_plot$plot <- delay60_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay60_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay60_plot$table <- delay60_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay60_plot$table
```


# KMs on All Patients
## 7) Survival status by Delay (60 days) and Stage
```{r, fig.width = 8, fig.height = 4}
delay60_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data_2018)

delay60_stage_plot <- ggsurvplot(fit = delay60_stage_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (60 days) and Stage",
  break.time.by = 3,
  palette = c("#E69F00", "#009E73", "#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("<60 days, Stage I-II", "<60 days, Stage III-IV", "≥60 days, Stage I-II", "≥60 days, Stage III-IV"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay60_stage_plot$plot <- delay60_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay60_stage_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay60_stage_plot$table <- delay60_stage_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay60_stage_plot$table
```


# KMs on All Patients
## 8) Survival status by Delay (30 days)
```{r, fig.width = 8}
delay30_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data_2018)

delay30_plot <- ggsurvplot(fit = delay30_survival,
  data_2018,
  xlab = "Months since treatment initiation",
  xlim = c(0, 24),
  ylab = "Proportion surviving",
  title = "Kaplan-Meier Survival Estimates by Delay (30 days)",
  break.time.by = 3,
  palette = c("#56B4E9", "#0072B2"),
  conf.int = FALSE,
  censor = TRUE,
  legend.title="",
  legend.labs = c("Delay <30 days", "Delay ≥30 days"),
  risk.table = TRUE,
  risk.table.height = 0.2,
  tables.theme = theme_cleantable())
delay30_plot$plot <- delay30_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), panel.grid.major.y = element_line(color = "#EAF2F3"), plot.background = element_rect(fill = "#EAF2F3"), axis.title.y = element_text(vjust = 1))

delay30_plot$plot
```
```{r, fig.height = 2, fig.width = 8}
delay30_plot$table <- delay30_plot$table + theme(plot.title = element_text(hjust = -0.25, size = 14), plot.background = element_rect(fill = "#EAF2F3"), panel.background = element_rect(fill = "#EAF2F3"))

delay30_plot$table
```

# Derived Survival Info
```{r}
## Median time
# Overall
data_2018 %>% summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (180 days)
data_2018 %>% group_by(path_treatment_180) %>%
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (150 days)
data_2018 %>% group_by(path_treatment_150) %>%
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (120 days)
data_2018 %>% group_by(path_treatment_120) %>% 
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (90 days)
data_2018 %>% group_by(path_treatment_90) %>% 
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (84 days)
data_2018 %>% group_by(path_treatment_84) %>% 
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (60 days)
data_2018 %>% group_by(path_treatment_60) %>% 
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (30 days)
data_2018 %>% group_by(path_treatment_30) %>% 
  dplyr::summarise(MedianCI(na.omit(time_alive_treat_mo)))


## 2 year survival
# Overall
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ 1, data_2018), times = c(2), extend = T)
# By delay (180 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data_2018)
# By delay (150 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data_2018)
# By delay (120 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data_2018)
# By delay (90 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_2018)
# By delay (84 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84, data_2018)
# By delay (60 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data_2018)
# By delay (30 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data_2018)

# By delay (120 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage_exact_factored4, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage_exact_factored4, data_2018)
# By delay (90 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage_exact_factored4, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage_exact_factored4, data_2018)
# By delay (60 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data_2018) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data_2018)

```