---
title: "Survival Analysis (Cox)"
author: "Jessica George and Shawna Tuli"
date: "3/25/2021"
output:
  html_document: default
  pdf_document: default
---

# Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(finalfit)
library(survival)
library(lubridate)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE}
data <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)
```

Treatment Delay Summary Stats
--------------------------------
Min = 0 days

Mean = 134 days (Max = 2,512 days!)

Median = 77 days

# Number of delays and Average Delay Time (d) per year
```{r}
data %>% 
  group_by(pathology_year) %>% 
  summarise("Number of Delays" = n(), 
            "Avg. Delay Time (d)" = mean(path_to_treatment_difference))
```

# Univariate Survival Results
```{r}
# Survival
dependent <- "Surv(time_alive_treat, vital_status)"

all_univariate <- c("init_performance_status", "marital", "alb_result", "distance", "age_cat", "hiv_status", "hiv_cd4_cat", "hiv_cd4_cat2", "hb_result", "combined_cancer_stage", "chemo", "total_chemo_received_4", "ebrt_40", "brachy_20", "eqd2", "path_to_treatment_difference", "path_treatment_120", "path_treatment_150", "path_treatment_180", "path_treatment_group")

data %>%
  finalfit(dependent, all_univariate) %>%
  select("Dependent: Surv(time_alive_treat, vital_status)", " ", "all", "HR (univariable)") %>% 
  knitr::kable()
```

# Univariate Survival Results
## Multivariate Survival Model 1
### Factors included: performance status, age category, HIV status, Hb, stage, path_to_treatment_difference
### AIC: 3134.537 -- Lowest AIC = Best Model!
``` {r}
all_multivariate1 <- c("init_performance_status", "age_cat", "hiv_status", "hb_result", "combined_cancer_stage", "path_to_treatment_difference")

data %>%
  finalfit(dependent, all_multivariate1) %>%
  select("Dependent: Surv(time_alive_treat, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_treat, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + combined_cancer_stage + path_to_treatment_difference, data = data))
```

## Multivariate Survival Model 2
### Factors included: performance status, age category, HIV status, Hb, stage, path_to_treatment_difference (90 day cutoff)
### AIC: 3135.131
``` {r}
all_multivariate2 <- c("init_performance_status", "age_cat", "hiv_status", "hb_result", "combined_cancer_stage", "path_treatment_90")

data %>%
  finalfit(dependent, all_multivariate2) %>%
  select("Dependent: Surv(time_alive_treat, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_treat, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + combined_cancer_stage + path_treatment_90, data = data))
```

## Multivariate Survival Model 3
### Factors included: performance status, age category, HIV status, Hb, stage, path_to_treatment_difference (120 day cutoff)
### AIC: 3135.278
``` {r}
all_multivariate3 <- c("init_performance_status", "age_cat", "hiv_status", "hb_result", "combined_cancer_stage", "path_treatment_120")

data %>%
  finalfit(dependent, all_multivariate3) %>%
  select("Dependent: Surv(time_alive_treat, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_treat, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + combined_cancer_stage + path_treatment_120, data = data))
```