---
title: "Figures - Kaplan-Meier"
author: "Jessica George"
date: "01/29/22"
output: 
  html_document:
    toc: True
    toc_depth: 2
---

# Libraries
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(survival)
library(survminer)
library(DescTools)
library(patchwork)
library(lubridate)
library(survRM2)

source("../../format_data.R")
```


# Data
```{r message=FALSE, warning=FALSE, include=FALSE}
data <- read_excel("../../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)
```

# KMs on All Patients
## 1) Survival status by Delay (180 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay180_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data)

delay180_plot <- ggsurvplot(fit = delay180_survival,
                            data,
                            xlab = "Months since treatment initiation",
                            xlim = c(0, 24),
                            ylab = "Proportion surviving",
                            title = "Kaplan-Meier Survival Estimates by Delay (180 days)",
                            break.time.by = 3,
                            palette = c("#56B4E9", "#0072B2"),
                            conf.int = FALSE,
                            censor = TRUE,
                            legend.title="",
                            legend.labs = c("Delay <180 days", "Delay ≥180 days"),
                            #legend.labs = c("No Delay", "Delay or Untreated"),
                            risk.table = TRUE,
                            risk.table.height = 0.2,
                            tables.theme = theme_cleantable())

delay180_plot$plot <- delay180_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay180_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay180_plot$table <- delay180_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay180_plot$table
```


## 2) Survival status by Delay (150 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay150_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data)

delay150_plot <- ggsurvplot(fit = delay150_survival,
                            data,
                            xlab = "Months since treatment initiation",
                            xlim = c(0, 24),
                            ylab = "Proportion surviving",
                            title = "Kaplan-Meier Survival Estimates by Delay (150 days)",
                            break.time.by = 3,
                            palette = c("#56B4E9", "#0072B2"),
                            conf.int = FALSE,
                            censor = TRUE,
                            legend.title="",
                            legend.labs = c("Delay <150 days", "Delay ≥150 days"),
                            #legend.labs = c("No Delay", "Delay or Untreated"),
                            risk.table = TRUE,
                            risk.table.height = 0.2,
                            tables.theme = theme_cleantable())

delay150_plot$plot <- delay150_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay150_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay150_plot$table <- delay150_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay150_plot$table
```


## 3) Survival status by Delay (120 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay120_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data)

delay120_plot <- ggsurvplot(fit = delay120_survival,
                            data,
                            xlab = "Months since treatment initiation",
                            #xlim = c(0, 24),
                            ylab = "Proportion surviving",
                            title = "Kaplan-Meier Survival Estimates by Delay (120 days)",
                            #break.time.by = 3,
                            palette = c("#56B4E9", "#0072B2"),
                            conf.int = FALSE,
                            censor = TRUE,
                            legend.title="",
                            legend.labs = c("Delay <120 days", "Delay ≥120 days"),
                            #legend.labs = c("No Delay", "Delay or Untreated"),
                            risk.table = TRUE,
                            risk.table.height = 0.2,
                            tables.theme = theme_cleantable())

delay120_plot$plot <- delay120_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay120_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay120_plot$table <- delay120_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay120_plot$table
```


## 4) Survival status by Delay (120 days) and Stage
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay120_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage2, data)

delay120_stage_plot <- ggsurvplot(fit = delay120_stage_survival,
                                  data,
                                  xlab = "Months since treatment initiation",
                                  xlim = c(0, 24),
                                  ylab = "Proportion surviving",
                                  title = "Kaplan-Meier Survival Estimates by Delay (120 days) and Stage",
                                  break.time.by = 3,
                                  palette = c("#E69F00", "#009E73", "#56B4E9",
                                              "#0072B2"),
                                  conf.int = FALSE,
                                  censor = TRUE,
                                  legend.title="",
                                  legend.labs = c("<120 days, Stage I-II", 
                                                  "<120 days, Stage III-IV", 
                                                  "≥120 days, Stage I-II", 
                                                  "≥120 days, Stage III-IV"),
                                  risk.table = TRUE,
                                  risk.table.height = 0.2,
                                  tables.theme = theme_cleantable())

delay120_stage_plot$plot <- delay120_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay120_stage_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay120_stage_plot$table <- delay120_stage_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay120_stage_plot$table
```


## 5) Survival status by Delay (90 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay90_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data)

delay90_plot <- ggsurvplot(fit = delay90_survival,
                           data,
                           xlab = "Months since treatment initiation",
                           xlim = c(0, 24),
                           ylab = "Proportion surviving",
                           title = "Kaplan-Meier Survival Estimates by Delay (90 days)",
                           break.time.by = 3,
                           palette = c("#56B4E9", "#0072B2"),
                           conf.int = FALSE,
                           censor = TRUE,
                           legend.title="",
                           legend.labs = c("Delay <90 days", "Delay ≥90 days"),
                           #legend.labs = c("No Delay", "Delay or Untreated"),
                           risk.table = TRUE,
                           risk.table.height = 0.2,
                           tables.theme = theme_cleantable())

delay90_plot$plot <- delay90_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay90_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay90_plot$table <- delay90_plot$table + 
  theme(plot.title = element_text(hjust = -0.24, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay90_plot$table

obj <- rmst2(data$time_alive_treat_mo, 
            data$vital_status, data$path_treatment_90_, tau=12)
print(obj)
```


## 6a) Survival status by Delay (90 days) and Stage
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay90_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage2, data)

print(delay90_stage_survival, print.rmean = TRUE)

delay90_stage_plot <- ggsurvplot(fit = delay90_stage_survival,
                                 data,
                                 xlab = "Months since treatment initiation",
                                 xlim = c(0, 24),
                                 ylab = "Proportion surviving",
                                 title = "Kaplan-Meier Survival Estimates by Delay (90 days) and Stage",
                                 break.time.by = 3,
                                 palette = c("#E69F00", "#009E73", 
                                             "#56B4E9", "#0072B2"),
                                 conf.int = FALSE,
                                 censor = TRUE,
                                 legend.title="",
                                 legend.labs = c("<90 days, Stage I-II", 
                                                 "<90 days, Stage III-IV", 
                                                 "≥90 days, Stage I-II", 
                                                 "≥90 days, Stage III-IV"),
                                 risk.table = TRUE,
                                 risk.table.height = 0.2,
                                 tables.theme = theme_cleantable())

delay90_stage_plot$plot <- delay90_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay90_stage_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay90_stage_plot$table <- delay90_stage_plot$table + 
  theme(plot.title = element_text(hjust = -0.15, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay90_stage_plot$table
```


## 6b) Survival status by Delay (90 days) and Stage
```{r echo=TRUE, fig.height=14, fig.width=16, message=FALSE, warning=FALSE}
data_stage1 <- data %>% 
  filter(combined_cancer_stage_exact_factored == "I (IA, IA1, IA2, IB1*, IB2, IB3)")

delay90_stage1_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage1)

delay90_stage1_plot <- ggsurvplot(fit = delay90_stage1_survival,
                                  data_stage1,
                                  xlab = "Months since treatment initiation",
                                  xlim = c(0, 24),
                                  ylab = "Proportion surviving",
                                  title = "Kaplan-Meier Survival Estimates for Stage I by Delay (90 days)",
                                  break.time.by = 3,
                                  palette = c("#E69F00", "#009E73"),
                                  color = "path_treatment_90",
                                  conf.int = FALSE,
                                  censor = TRUE,
                                  legend="none",
                                  legend.title="",
                                  legend.labs = c("<90 days", "≥90 days"),
                                  risk.table = TRUE,
                                  risk.table.height = 0.2,
                                  tables.theme = theme_cleantable())

delay90_stage1_plot$plot <- delay90_stage1_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

data_stage2 <- data %>% 
  filter(combined_cancer_stage_exact_factored == "II (IIA / IIB)")

delay90_stage2_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage2)

delay90_stage2_plot <- ggsurvplot(fit = delay90_stage2_survival,
                                  data_stage2,
                                  xlab = "Months since treatment initiation",
                                  xlim = c(0, 24),
                                  ylab = "Proportion surviving",
                                  title = "Kaplan-Meier Survival Estimates for Stage II by Delay (90 days)",
                                  break.time.by = 3,
                                  palette = c("#E69F00", "#009E73"),
                                  color = "path_treatment_90",
                                  conf.int = FALSE,
                                  censor = TRUE,
                                  legend="none",
                                  legend.title="",
                                  legend.labs = c("<90 days", "≥90 days"),
                                  risk.table = TRUE,
                                  risk.table.height = 0.2,
                                  tables.theme = theme_cleantable())

delay90_stage2_plot$plot <- delay90_stage2_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

data_stage3 <- data %>% 
  filter(combined_cancer_stage_exact_factored == "III (IIIA / IIIB / IIIC)")

delay90_stage3_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage3)

delay90_stage3_plot <- ggsurvplot(fit = delay90_stage3_survival,
                                  data_stage3,
                                  xlab = "Months since treatment initiation",
                                  xlim = c(0, 24),
                                  ylab = "Proportion surviving",
                                  title = "Kaplan-Meier Survival Estimates for Stage III by Delay (90 days)",
                                  break.time.by = 3,
                                  palette = c("#E69F00", "#009E73"),
                                  color = "path_treatment_90",
                                  conf.int = FALSE,
                                  censor = TRUE,
                                  legend="none",
                                  legend.title="",
                                  legend.labs = c("<90 days", "≥90 days"),
                                  risk.table = TRUE,
                                  risk.table.height = 0.2,
                                  tables.theme = theme_cleantable())

delay90_stage3_plot$plot <- delay90_stage3_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

data_stage4 <- data %>% 
  filter(combined_cancer_stage_exact_factored == "IV (IVA / IVB)")

delay90_stage4_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data_stage4)

delay90_stage4_plot <- ggsurvplot(fit = delay90_stage4_survival,
                                  data_stage4,
                                  xlab = "Months since treatment initiation",
                                  xlim = c(0, 24),
                                  ylab = "Proportion surviving",
                                  title = "Kaplan-Meier Survival Estimates for Stage IV by Delay (90 days)",
                                  break.time.by = 3,
                                  palette = c("#E69F00", "#009E73"),
                                  color = "path_treatment_90",
                                  conf.int = FALSE,
                                  censor = TRUE,
                                  legend="none",
                                  legend.title="",
                                  legend.labs = c("<90 days", "≥90 days"),
                                  risk.table = TRUE,
                                  risk.table.height = 0.2,
                                  tables.theme = theme_cleantable())

delay90_stage4_plot$plot <- delay90_stage4_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay90_stage1_plot$plot + delay90_stage2_plot$plot + 
  delay90_stage3_plot$plot + delay90_stage4_plot$plot +
  plot_layout(guides = 'collect') & 
  theme(legend.title = element_blank(), legend.position = 'top')
```


## 7) Survival status by Delay (90 days) and Palliative/Curative/Definitive
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay90_cpd_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + curative_palliative, data)

delay90_cpd_plot <- ggsurvplot(fit = delay90_cpd_survival,
                               data,
                               xlab = "Months since treatment initiation",
                               xlim = c(0, 24),
                               ylab = "Proportion surviving",
                               title = "Kaplan-Meier Survival Estimates by Delay (90 days) and Treatment",
                               break.time.by = 3,
                               #palette = c("#E69F00", "#009E73", 
                                           #"#56B4E9", "#0072B2"),
                               conf.int = FALSE,
                               censor = TRUE,
                               legend.title="",
                               legend.labs = c("<90 days, Palliative", 
                                               "<90 days, Curative", 
                                               "<90 days, Definitive", 
                                               "≥90 days, Palliative",
                                               "≥90 days, Curative",
                                               "≥90 days, Definitive"),
                              risk.table = TRUE,
                              risk.table.height = 0.2,
                              tables.theme = theme_cleantable())

delay90_cpd_plot$plot <- delay90_cpd_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay90_cpd_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay90_cpd_plot$table <- delay90_cpd_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay90_cpd_plot$table
```


## 8) Survival status by Delay (60 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay60_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data)

delay60_plot <- ggsurvplot(fit = delay60_survival,
                           data,
                           xlab = "Months since treatment initiation",
                           xlim = c(0, 24),
                           ylab = "Proportion surviving",
                           title = "Kaplan-Meier Survival Estimates by Delay (60 days)",
                           break.time.by = 3,
                           palette = c("#56B4E9", "#0072B2"),
                           conf.int = FALSE,
                           censor = TRUE,
                           legend.title="",
                           legend.labs = c("Delay <60 days", "Delay ≥60 days"),
                           risk.table = TRUE,
                           risk.table.height = 0.2,
                           tables.theme = theme_cleantable())

delay60_plot$plot <- delay60_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay60_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay60_plot$table <- delay60_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay60_plot$table
```


## 9) Survival status by Delay (60 days) and Stage
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay60_stage_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data)

delay60_stage_plot <- ggsurvplot(fit = delay60_stage_survival,
                                 data,
                                 xlab = "Months since treatment initiation",
                                 xlim = c(0, 24),
                                 ylab = "Proportion surviving",
                                 title = "Kaplan-Meier Survival Estimates by Delay (60 days) and Stage",
                                 break.time.by = 3,
                                 palette = c("#E69F00", "#009E73", "#56B4E9", "#0072B2"),
                                 conf.int = FALSE,
                                 censor = TRUE,
                                 legend.title="",
                                 legend.labs = c("<60 days, Stage I-II", 
                                                 "<60 days, Stage III-IV", 
                                                 "≥60 days, Stage I-II", "≥60 days, Stage III-IV"),
                                risk.table = TRUE,
                                risk.table.height = 0.2,
                                tables.theme = theme_cleantable())

delay60_stage_plot$plot <- delay60_stage_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay60_stage_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay60_stage_plot$table <- delay60_stage_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay60_stage_plot$table
```


## 10) Survival status by Delay (30 days)
```{r echo=TRUE, fig.width=8, message=FALSE, warning=FALSE}
delay30_survival <- survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data)

delay30_plot <- ggsurvplot(fit = delay30_survival,
                           data,
                           xlab = "Months since treatment initiation",
                           xlim = c(0, 24),
                           ylab = "Proportion surviving",
                           title = "Kaplan-Meier Survival Estimates by Delay (30 days)",
                           break.time.by = 3,
                           palette = c("#56B4E9", "#0072B2"),
                           conf.int = FALSE,
                           censor = TRUE,
                           legend.title="",
                           legend.labs = c("Delay <30 days", "Delay ≥30 days"),
                           risk.table = TRUE,
                           risk.table.height = 0.2,
                           tables.theme = theme_cleantable())

delay30_plot$plot <- delay30_plot$plot +
  theme(plot.title = element_text(hjust = 0.4), 
        panel.grid.major.y = element_line(color = "#EAF2F3"), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        axis.title.y = element_text(vjust = 1))

delay30_plot$plot
```
```{r echo=TRUE, fig.height=2, fig.width=8, message=FALSE, warning=FALSE}
delay30_plot$table <- delay30_plot$table + 
  theme(plot.title = element_text(hjust = -0.25, size = 14), 
        plot.background = element_rect(fill = "#EAF2F3"), 
        panel.background = element_rect(fill = "#EAF2F3"))

delay30_plot$table
```


# Derived Survival Info
```{r echo=TRUE, message=FALSE, warning=FALSE}
## Median time
# Overall
data %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (180 days)
data %>% 
  group_by(path_treatment_180) %>%
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (150 days)
data %>% 
  group_by(path_treatment_150) %>%
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (120 days)
data %>% 
  group_by(path_treatment_120) %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (90 days)
data %>% 
  group_by(path_treatment_90) %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (84 days)
data %>% 
  group_by(path_treatment_84) %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (60 days)
data %>% 
  group_by(path_treatment_60) %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))
# By delay (30 days)
data %>% 
  group_by(path_treatment_30) %>% 
  summarise(MedianCI(na.omit(time_alive_treat_mo)))


## 2 year survival
# Overall
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ 1, data), times = c(2), extend = T)
# By delay (180 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_180, data)
# By delay (150 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_150, data)
# By delay (120 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120, data)
# By delay (90 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90, data)
# By delay (84 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_84, data)
# By delay (60 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60, data)
# By delay (30 days)
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_30, data)

# By delay (120 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage_exact_factored4, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_120 + combined_cancer_stage_exact_factored4, data)
# By delay (90 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage_exact_factored4, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_90 + combined_cancer_stage_exact_factored4, data)
# By delay (60 days) and stage
summary(survfit(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data) , times = c(2), extend = T)
survdiff(Surv(time_alive_treat_mo, vital_status) ~ path_treatment_60 + combined_cancer_stage_exact_factored4, data)
```