---
title: "Table 2"
author: "Jessica George and Shawna Tuli"
date: "3/15/2021"
output:
  html_document: default
  pdf_document: default
---

# Libraries
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(finalfit)
library(lubridate)
library(survival)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE, include=FALSE}
data <- read_csv("../../data/data.csv") %>% 
  format_data(article_number = 1)
```

# Univariate Results
```{r}
dependent <- "Surv(time_alive_path, vital_status)"

all_univariate <- c("init_performance_status", "marital", "alb_result", "distance", "age_cat", "hiv_status", "hiv_cd4_cat2", "hb_result", "combined_cancer_stage", "vl_detect_cat")

data %>%
  finalfit(dependent, all_univariate) %>%
  select("Dependent: Surv(time_alive_path, vital_status)", " ", "all", "HR (univariable)") %>% 
  knitr::kable()
```


# Initial Multivariate Models (1-4)

## Multivariate Model 1
### Factors: performance status, age (category), HIV status, Hb, and stage
### AIC: 3940.583
```{r}
all_multivariate1 <- c("init_performance_status", "age_cat", "hiv_status", "hb_result", "combined_cancer_stage")

data %>%
  finalfit(dependent, all_multivariate1) %>%
  select("Dependent: Surv(time_alive_path, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + combined_cancer_stage, data = data))
```

## Multivariate Model 2
### Factors: performance status, age (category), HIV-CD4 (category), Hb, and stage
### AIC: 3326.612
``` {r}
all_multivariate2 <- c("init_performance_status", "age_cat", "hiv_cd4_cat2", "hb_result", "combined_cancer_stage")

data %>%
  finalfit(dependent, all_multivariate2) %>%
    select("Dependent: Surv(time_alive_path, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_cd4_cat2 + hb_result + combined_cancer_stage, data = data))
```

## Multivariate Model 3
### Factors: performance status, age (category), HIV-CD4 (category), Hb, Alb, VL, and stage
### AIC: 2236.844
``` {r}
all_multivariate3 <- c("init_performance_status", "age_cat", "hiv_cd4_cat2", "hb_result", "combined_cancer_stage", "vl_detect2", "alb_result")

data %>%
  finalfit(dependent, all_multivariate3) %>%
    select("Dependent: Surv(time_alive_path, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_cd4_cat2 + hb_result + combined_cancer_stage + vl_detect2 + alb_result, data = data))
```

## Multivariate Model 4
### Factors: performance status, age (category), HIV-CD4 (category), Hb, Alb, and stage
### AIC: 2233.012 -- Lower AIC = Better model!
``` {r}
all_multivariate4 <- c("init_performance_status", "age_cat", "hiv_cd4_cat2", "hb_result", "combined_cancer_stage", "alb_result")

data %>%
  finalfit(dependent, all_multivariate4) %>%
    select("Dependent: Surv(time_alive_path, vital_status)", " ", "all", "HR (multivariable)") %>% 
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_cd4_cat2 + hb_result + combined_cancer_stage + alb_result, data = data))
```


# Final Models

## Survival Model
```{r}
all_multivariate <- c("init_performance_status", "age_cat", "hiv_status", "hb_result", "alb_result", "combined_cancer_stage")

data %>%
  finalfit(dependent, all_multivariate) %>%
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + alb_result + combined_cancer_stage, data = data))
```

## Supplemental Survival Model
```{r}
all_multivariate_sup <- c("init_performance_status", "age_cat", "hiv_cd4_cat2", "hb_result", "alb_result", "combined_cancer_stage")

data %>%
  finalfit(dependent, all_multivariate_sup) %>%
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_cd4_cat2 + hb_result + combined_cancer_stage, data = data))
```

## Survival Model on Treatment Patients
```{r}
treated <- data %>% 
  filter(treatment == "Yes")

treated %>%
  finalfit(dependent, all_multivariate) %>%
  knitr::kable()

AIC(coxph(Surv(time_alive_path, vital_status) ~ init_performance_status + age_cat + hiv_status + hb_result + alb_result + combined_cancer_stage, data = treated))
```