---
title: "Binomial Logistic Regression"
author: "Jessica George and Shawna Tuli"
date: "4/11/2021"
output:
  html_document: default
  pdf_document: default
---

# Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(finalfit)
library(survival)
library(lubridate)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE}
data <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)
```

# Functions
```{r}
overall_univariate_logistic_regresion <- function(resp, predictors) {
  formula <- as.formula(paste(resp, predictors, sep = " ~ "))
  overall.logist <- glm(formula, data = data, family = binomial)
  return(overall.logist)
}

overall_multivariate_logistic_regresion <- function(resp, predictors) {
  formula <- as.formula(paste(resp, paste(predictors, collapse = " + "), sep = " ~ "))
  overall.logist <- glm(formula, data = data, family = binomial)
  return(overall.logist)
}
```

# Univariate Models
```{r results="asis"}
uni_predictors <- c("enroll_age", "age_cat", "marital", "distance", "init_performance_status", "hiv_status", "hiv_cd4_cat", "hiv_cd4_cat2", "hb_result", "wbc_result", "alb_result", "combined_cancer_stage", "total_chemo_received", "total_chemo_received_4", "eqd2", "eqd2_75", "ebrt_40", "pathology_group", "cancer_screening")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  for (uni_predictor in uni_predictors) {
    if (resp == "path_treatment_120") {
      cat("\n## Path to Treatment Time Difference (120 days) ~ ", uni_predictor, "  \n")
    }
    else if (resp == "path_treatment_150") {
      cat("\n## Path to Treatment Time Difference (150 days) ~ ", uni_predictor, "  \n")
    }
    else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", uni_predictor, "  \n") }
      model <- overall_univariate_logistic_regresion(resp, uni_predictor)
      cat("```")
      print(summary(model))
      print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
      cat("```")  
  }
}
```

# Multivariate Models

## Baseline Only (No Treatment Included)
### Age, performance status, HIV status, Hb, stage 
```{r results="asis"}
multi_predictors <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "combined_cancer_stage")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}

```
### Age, performance status, HIV status, WBC, stage
```{r results="asis"}
multi_predictors <- c("age_cat", "init_performance_status", "hiv_status", "wbc_result", "combined_cancer_stage")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```
### Age, performance status, HIV status, Hb, WBC, stage
```{r results="asis"}
multi_predictors <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "wbc_result", "combined_cancer_stage")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```
### Age, performance status, HIV status, Albumin, stage
```{r results="asis"}
multi_predictors <- c("age_cat", "init_performance_status", "hiv_status", "alb_result", "combined_cancer_stage")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```

## Treatment Included
### Age, performance status, HIV status, Hb, stage, chemo (4 cycles), RT 
```{r results="asis"}
multi_predictors1 <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "combined_cancer_stage", "total_chemo_received_4", "eqd2")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors1)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}

# eqd2 --> ebrt
multi_predictors2 <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "combined_cancer_stage", "total_chemo_received_4", "ebrt_40")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors2)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```
### Age, performance status, HIV status, WBC, stage, chemo (4 cycles), RT 
```{r results="asis"}
multi_predictors1 <- c("age_cat", "init_performance_status", "hiv_status", "wbc_result", "combined_cancer_stage", "total_chemo_received_4", "eqd2")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors1)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}

# eqd2 --> ebrt
multi_predictors2 <- c("age_cat", "init_performance_status", "hiv_status", "wbc_result", "combined_cancer_stage", "total_chemo_received_4", "ebrt_40")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors2)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```
### Age, performance status, HIV status, Hb, WBC, stage, chemo (4 cycles), RT 
```{r results="asis"}
multi_predictors1 <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "wbc_result", "combined_cancer_stage", "total_chemo_received_4", "eqd2")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors1)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}

# eqd2 --> ebrt
multi_predictors2 <- c("age_cat", "init_performance_status", "hiv_status", "hb_result", "wbc_result", "combined_cancer_stage", "total_chemo_received_4", "ebrt_40")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors2)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```
### Age, performance status, HIV status, Albumin, stage, chemo (4 cycles), RT 
```{r results="asis"}
multi_predictors1 <- c("age_cat", "init_performance_status", "hiv_status", "alb_result", "combined_cancer_stage", "total_chemo_received_4", "eqd2")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors1, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors1)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}

# eqd2 --> ebrt
multi_predictors2 <- c("age_cat", "init_performance_status", "hiv_status", "alb_result", "combined_cancer_stage", "total_chemo_received_4", "ebrt_40")

for (resp in c("path_treatment_120", "path_treatment_150", "path_treatment_180")) {
  if (resp == "path_treatment_120") {
    cat("\n## Path to Treatment Time Difference (120 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else if (resp == "path_treatment_150") {
    cat("\n## Path to Treatment Time Difference (150 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n")
  }
  else { cat("\n## Path to Treatment Time Difference (180 days) ~ ", paste(multi_predictors2, collapse = " + "), "  \n") }
  model <- overall_multivariate_logistic_regresion(resp, multi_predictors2)
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")  
}
```