---
title: "Multinomial Logistic Regression"
author: "Jessica George and Shawna Tuli"
date: "4/13/2021"
output: html_document
---

# Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(survival)
library(lubridate)
library(nnet)
library(knitr)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE}
data <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)
```

# Functions
```{r}
overall_univariate_logistic_regresion <- function(resp, predictors) {
  formula <- as.formula(paste(resp, predictors, sep = " ~ "))
  overall.logist <- multinom(formula, data = data)
  return(overall.logist)
}

overall_multivariate_logistic_regresion <- function(resp, predictors) {
  formula <- as.formula(paste(resp, paste(predictors, collapse = " + "), sep = " ~ "))
  overall.logist <- multinom(formula, data = data)
  return(overall.logist)
}
```

# Univariate Models
```{r results="asis"}
uni_predictors <- c("enroll_age", "age_cat", "marital", "distance", "init_performance_status", "hiv_status", "hiv_cd4_cat", "hiv_cd4_cat2", "hb_result", "wbc_result", "alb_result", "combined_cancer_stage", "total_chemo_received", "total_chemo_received_4", "eqd2", "eqd2_75", "ebrt_40", "pathology_year", "cancer_screening")

for (resp in c("path_treatment_group")) {
  for (uni_predictor in uni_predictors) {
    cat("\n## Path to Treatment Time Difference Group ~ ", uni_predictor, "  \n")
    model <- overall_univariate_logistic_regresion(resp, uni_predictor)
    cat("```")
    model_summary <- summary(model)
    print(model_summary)
    z <- model_summary$coefficients/model_summary$standard.errors
    p <- (1 - pnorm(abs(z), 0, 1))*2 # two-tailed z test
    output <- rbind(model_summary$coefficients[1,], model_summary$standard.errors[1,], z[1,], p[1,])
    rownames(output) <- c("Coefficient","Std. Errors","z stat","p value")
    #kable(output)
    print(output)
    print(exp(coef(model)))
    cat("```")  
  }
}
```