---
title: "Upstaging"
author: "Jessica George and Shawna Tuli"
date: "4/11/2021"
output: html_document
---

# Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(finalfit)
library(survival)
library(lubridate)

source("../format_data.R")
```

# Data
```{r message=FALSE, warning=FALSE}
data <- read_excel("../../data/time_to_treatment_data.xlsx") %>% 
  format_data(article_number = 3)
```

# Time to treatment < 90 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 351 patients

data %>% 
  # Filter for people with time to treatment < 90 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference < 90 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/351)*100)
```

# Time to treatment >= 90 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 204 patients

data %>% 
  # Filter for people with time to treatment => 120 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference >= 90 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/204)*100)
```

# Time to treatment < 120 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 418 patients

data %>% 
  # Filter for people with time to treatment < 120 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference < 120 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/418)*100)
```

# Time to treatment >= 120 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 137 patients

data %>% 
  # Filter for people with time to treatment => 120 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference >= 120 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/137)*100)
```

# Time to treatment < 150 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 453 patients

data %>% 
  # Filter for people with time to treatment < 150 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference < 150 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/453)*100)
```

# Time to treatment >= 150 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 102 patients

data %>% 
  # Filter for people with time to treatment => 150 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference >= 150 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/102)*100)
```

# Time to treatment < 180 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 467 patients

data %>% 
  # Filter for people with time to treatment < 180 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference < 180 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/490)*100)
```

# Time to treatment >= 180 days
## Only large data patients have fin figo (small only has init figo) (495 patients with no NA for fin figo)
```{r}
# 88 patients

data %>% 
  # Filter for people with time to treatment => 180 days
  # Second filter removes small data patients
  filter(path_to_treatment_difference >= 180 & !is.na(final_cancer_stage_exact)) %>% 
  mutate(
    init_cancer_stage_exact = as.numeric(init_cancer_stage_exact),
    final_cancer_stage_exact = as.numeric(final_cancer_stage_exact),
    stage_difference = final_cancer_stage_exact - init_cancer_stage_exact) %>% 
  # Filter for upstaging
  filter(stage_difference > 0) %>% 
  summarise("Upstaged (%)" = (n()/88)*100)
```