---
title: "Logistic Regression"
author: "Shawna Tuli and Jessica George"
date: "01/20/22"
output: 
  html_document:
    toc: True
    toc_depth: 1
---

# Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(survival)
library(Table1)

source("../format_data.R")
```


# Data
```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("../../data/data.csv") %>% 
  format_data(article_number = 2)
```


# Create binary response variables
```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- data %>%
  mutate(
    hb_response = factor(case_when(hb_tox_grade <= 1 ~ 0,
                                   hb_tox_grade > 1 ~ 1)),
    cr_response = factor(case_when(cr_tox_grade <= 1 ~ 0,
                                   cr_tox_grade > 1 ~ 1)),
    neut_response = factor(case_when(neut_tox_grade <= 1 ~ 0,
                                     neut_tox_grade > 1 ~ 1)),
    wbc_response = factor(case_when(wbc_tox_grade <= 1 ~ 0,
                                    wbc_tox_grade > 1 ~ 1)),
    alb_response = factor(case_when(alb_tox_grade <= 1 ~ 0,
                                    alb_tox_grade > 1 ~ 1)),
    GI_response = factor(case_when(nausea_tox <= 1 | 
                                     vomiting_tox <= 1 | 
                                     diarrhea_tox <= 1 ~ 0,
                                   nausea_tox > 1 | 
                                     vomiting_tox > 1 | 
                                     diarrhea_tox > 1 ~ 1)),
    GU_response = factor(case_when(urine_freq_tox <= 1 | 
                                     urine_incontinence_tox <= 1 |
                                     urine_urge_tox <= 1 ~ 0,
                                   urine_freq_tox > 1 | 
                                     urine_incontinence_tox > 1 | 
                                     urine_urge_tox > 1 ~ 1)),
    vaginal_response = factor(case_when(vaginal_hemorrhage_tox <= 1 |
                                          vaginal_discharge_tox <= 1 |
                                          pelvic_pain_tox <= 1 ~ 0,
                                        vaginal_hemorrhage_tox > 1 |
                                          vaginal_discharge_tox > 1 |
                                          pelvic_pain_tox > 1 ~ 1)),
    fatigue_response = factor(case_when(fatigue_tox <= 1 ~ 0,
                                        fatigue_tox > 1 ~ 1)),
    dermatitis_response = factor(case_when(dermatitis_tox <= 1 ~ 0,
                                           dermatitis_tox > 1 ~ 1))
  )
```


# Functions
```{r echo=TRUE, message=FALSE, warning=FALSE}
overall_univariate_logistic_regression <- function(resp, predictors) {
  formula <- as.formula(paste(resp, predictors, sep = " ~ "))
  overall.logist <- glm(formula, data = data, family = binomial)
  return(overall.logist)
}

subset_univariate_logistic_regression <- function(resp, predictors, group) {
  formula <- as.formula(paste(resp, predictors, sep = " ~ "))
  res.logist <- glm(formula, data = data, family = binomial, 
                    subset = hiv_status == group)
  return(res.logist)
}

overall_multivariate_logistic_regression <- function(resp, predictors) {
  formula <- as.formula(paste(resp, paste(predictors, collapse = " + "), 
                              sep = " ~ "))
  overall.logist <- glm(formula, data = data, family = binomial)
  return(overall.logist)
}

subset_multivariate_logistic_regression <- function(resp, predictors, group) {
  formula <- as.formula(paste(resp, paste(predictors, collapse = " + "), 
                              sep = " ~ "))
  res.logist <- glm(formula, data = data, family = binomial, 
                    subset = hiv_status == group)
  return(res.logist)
}
```


# Univariate Logistic Regression
```{r echo=TRUE, message=FALSE, warning=FALSE, results="asis"}
responses <- c("hb_response", "cr_response", "neut_response", "wbc_response", "alb_response", "GI_response", "GU_response", "vaginal_response", "fatigue_response", "dermatitis_response")

uni_predictors <- c("age_cat", "combined_cancer_stage", "eqd2", "total_chemo_received_4", "eqd2", "nrti", "pi", "cd4_pos_cat2", "cd4_final", "vl_final", "azt", "tdf")

for (uni_predictor in uni_predictors) {
  for (response in responses) {
    cat("\n##", response, "~", uni_predictor, "  \n")
    model <- subset_univariate_logistic_regression(response, uni_predictor, "HIV-infected")
    cat("```")
    print(summary(model))
    # Skip outputting OR on sparse data
    if (response == "GU_response" & uni_predictor %in% c("cd4_final", "vl_final", "cd4_pos_cat2", "azt", "tdf")) {
      cat("```")
      next
    }
    print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
    cat("```")
  }
}
 
for (response in responses) {
  cat("\n##", response, "~ nnrti + pi  \n")
  model <- subset_multivariate_logistic_regression(response, c("nnrti", "pi"), "HIV-infected")
  cat("```")
  print(summary(model))
  print(exp(cbind(OR = coef(model), suppressMessages(confint(model)))))
  cat("```")
}
```